---
output:
  github_document
---

## Quarto Manuscript

<!-- badges: start -->
[![paper](https://github.com/sds-capstone/quarto-manuscript/actions/workflows/publish.yml/badge.svg)](https://github.com/sds-capstone/quarto-manuscript/actions/workflows/publish.yml)
<!-- badges: end -->

You can view the published work at:
<https://sds-capstone.github.io/quarto-manuscript/>

## Note

This is a template repo for generating a manuscript from Quarto that accompanies the tutorial at: [Quarto Manuscripts: RStudio](https://quarto.org/docs/manuscripts/authoring/rstudio.html)

## Repository analysis via `chchchanges`

### Current as of: `r format(Sys.time(), "%B %e, %Y, %H:%M:%S")`

Here is a summary of the commits made to this repository:

```{r tbl}
chchchanges::summarize_commits() |>
  knitr::kable()
```


The following analysis is automated via [Google Gemini](https://en.wikipedia.org/wiki/Gemini_(chatbot)) and the [`chchchanges`](https://github.com/beanumber/chchchanges) package. 

```{r llm, results='asis'}
chchchanges::summarize_git_with_llm(
  show_prompts = TRUE, 
  user_prompt = "Also assign letter grades to each contributor. "
) |>
  markdown::mark()
```

